miniKanren with fair search

### 2019-03-17 Paper/paper.tex
update abstract

\title{BFS search in miniKanren}
\author{Kuang-Chen Lu}
\affiliation{Indiana University}
\author{Weixi Ma}
\affiliation{Indiana University}
\author{Daniel P. Friedman}
\affiliation{Indiana University}

@@

The syntax of a programming language should reflect its semantics.
When using a disjunction operator in relational programming, a programmer would
expect all clauses of this disjunction to share the same chance of being explored,
as these clauses are written in parallel. The existing disjunctive operators in
miniKanren, however, prioritize their clauses by the order of which these clauses are
written down. We have devised a new search strategy that searches evenly in all
clauses. Based on our statistics, miniKanren slows down by a constant factor after
applying our search strategy.
(tested with very-recursiveo, need more tests)

%TODO update "result" once having more test cases: quine, '(I love you).

>>>>

\title{miniKanren with fair search}
\author{Kuang-Chen Lu}
\affiliation{Indiana University}
\author{Weixi Ma}
\affiliation{Indiana University}
\author{Daniel P. Friedman}
\affiliation{Indiana University}

@@

The syntax of a programming language should reflect its semantics.
When using a disjunction operator in relational programming, a programmer would
expect all clauses of this disjunction to share the same chance of being explored,
as these clauses are written in parallel. 
% The existing disjunctive operators in miniKanren, however, prioritize their clauses
The existing multiarity disjunctive operator in miniKanren, however, prioritize its clauses
by the order of which these clauses are written down. 
% We have devised a new search strategy that searches evenly in all clauses.
We have devised two new search strategies that allocate computational effort fairly in all clauses.

(TODO: evaluation of performance)

%TODO test cases: quine, '(I love you).
